--- 
title: "World Analysis on Energy, Food and Population"
author: "Gorkem Tunc"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: openscapes/series
description: "An analysis about the energy production bases on which energy source or type, food production increase in time and population increase since 1950"
---

# TP about World Energy, Food and Population Datasets



```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(lubridate)
library(readxl)
library(tidyselect)

setwd("C:/Users/gorke/Desktop/CEFIM_formation/Data_Analyst/R_Studio/Seq_TP")

```


## Analysis General

### Chart Energy per Source

```{r}

energy_source <- read_delim("energy_source.csv") |> 
  filter(country=="World")|> 
  filter(type_energie!="primary_energy_consumption",
         type_energie!="fossil_fuel_consumption",
         type_energie!="low_carbon_consumption",
         type_energie!="renewables_consumption",
         type_energie!="other_renewable_consumption")

ggplot(energy_source)+ 
  aes(year,consommation,fill=type_energie)+
  geom_col()

```

### Chart Energy per Type

```{r}

energy_type <- read_delim("energy_type.csv") |> 
  filter(country=="World")|> 
  filter(type_energie=="fossil_fuel_consumption"|
         type_energie=="low_carbon_consumption"|
         type_energie=="renewables_consumption"|
         type_energie=="other_renewable_consumption") 

ggplot(energy_type)+ 
  aes(year,consommation,colour=type_energie)+
  geom_line()+
  geom_col(aes(fill=type_energie))



```


### Chart World Food Production

```{r fig.width=20}

production_world <- read_delim("production_world.csv") |> 
  filter(Area=="World", 
         Element=="Production") |> 
  filter(str_detect(Item,"Total")|str_detect(Item,"Primary"))

ggplot(production_world)+
  aes(annee,valeur,colour=Item)+
  geom_point()+
  geom_line()

```

### Chart Evolution of World Population

```{r}

population_world_total <- read_delim("population_world_total.csv") |> 
  filter(Type=="World") # filtering to get only the world data

ggplot(population_world_total)+
  aes(annee,population)+
  geom_point()+
  geom_line(aes(group=1))+
  scale_y_continuous(labels=function(x) {
    format(x,scientific=FALSE,
           big.mark=" ")
  })

```


## Analysis Per Continent

### Chart Energy per Source per Continent

```{r}

energy_continent_g1 <- read_delim("energy_countrycode.csv") |> 
  filter(!is.na(continent))|> 
  filter(year >= 1950) |> 
  filter(type_energie!="primary_energy_consumption",
         type_energie!="fossil_fuel_consumption",
         type_energie!="low_carbon_consumption",
         type_energie!="renewables_consumption",
         type_energie!="other_renewable_consumption") |> 
  group_by(year,continent,type_energie) |> 
  summarise(consommation_sum_type=sum(consommation,na.rm = TRUE))

ggplot(energy_continent_g1)+ 
  aes(year,consommation_sum_type,fill=type_energie)+
  geom_col()+
  facet_grid(~continent)+
  theme(axis.text.x=element_text(size=6,
                                 angle=45,
                                 hjust=1,
                                 vjust=1))
```

### Chart Energy per Type per Continent

```{r}

energy_continent_g2 <- read_delim("energy_countrycode.csv") |> 
  filter(!is.na(continent))|> 
  filter(year >= 1950) |> 
  filter(type_energie=="fossil_fuel_consumption"|
         type_energie=="low_carbon_consumption"|
         type_energie=="renewables_consumption"|
         type_energie=="other_renewable_consumption") |> 
  group_by(year,continent,type_energie) |> 
  summarise(consommation_sum_source=sum(consommation,na.rm = TRUE))

ggplot(energy_continent_g2)+
  aes(year,consommation_sum_source,colour=type_energie)+
  geom_line()+
  geom_col(aes(fill=type_energie))+
  facet_grid(~continent)+
  theme(axis.text.x=element_text(size=6,
                                 angle=45,
                                 hjust=1,
                                 vjust=1))


```


### Chart World Food Production per Continent

```{r fig.width=20}

production_continent <- read_delim("food_countrycode.csv") |> 
  filter(!is.na(Continent)) |> 
  filter(Element=="Production") |> 
  filter(str_detect(Item,"Total")|str_detect(Item,"Primary")) |> 
  group_by(Continent,annee) |> 
  summarise(continent_sum_food=sum(valeur,na.rm = TRUE))


ggplot(production_continent)+
  aes(annee,continent_sum_food,colour=Continent)+
  geom_point()+
  geom_line()+
  facet_grid(~Continent)+
  theme(axis.text.x=element_text(size=6,
                                 angle=45,
                                 hjust=1,
                                 vjust=1))+
  scale_y_continuous(labels=function(x) {
    format(x,scientific=FALSE,
           big.mark=" ")
  })

```

### Chart Evolution of World Population per Continent

```{r}

population_continent <- read_delim("population_countrycode.csv") |> 
  filter(!is.na(Continent)) |> 
  group_by(Continent,annee) |> 
  summarise(continent_sum_pop=sum(population,na.rm = TRUE))
  
ggplot(population_continent)+
  aes(annee,continent_sum_pop,fill=Continent)+
  geom_col()+
  geom_line(aes(group=Continent))+
  scale_y_continuous(labels=function(x) {
    format(x,scientific=FALSE,
           big.mark=" ")
  })+
  facet_grid(~Continent)+
  theme(axis.text.x=element_text(size=6,
                                 angle=90,
                                 hjust=1,
                                 vjust=1))

```

```{r}

knitr::include_app("https://gorkemtunc.shinyapps.io/Shiny_Web_App/")



```






